\textbf{How open are hybrid journals included in transformative agreements?}

### 2024-02-28 analysis/manuscript.tex
minor

%\authornote{Correspondence concerning this article should be addressed to Najko Jahn}

\abstract{}

@@

Despite these controversies around transformative agreements as a means
of transitioning journal publishing to full open access, there is
limited evidence available on the adoption of open access in hybrid
journals, and the extent to which this can be attributed to
transformative agreements. Previous studies have focused on specific
countries (Haucap et al., 2021; Huang et al., 2020; Pölönen et al.,
2020; Taubert et al., 2023; Wenaas, 2022) or publisher portfolios
(Bakker et al., 2024; Fraser et al., 2023; Jahn et al., 2022; Momeni et
al., 2023; Pieper \& Broschinski, 2018; Schmal, 2024), while large-scale
studies relied on self-reported agreement data (Moskovkin et al., 2022),
or used APC pricing lists (Shu \& Larivière, 2023). In particular, data
availability is a limiting factor when studying the impact of
transformative agreements (Bakker et al., 2024), because bibliometric
databases, even though many allow the retrieval of open access articles
in hybrid journals, do not directly attribute them to specific
transformative agreements. Likewise, article-level open access invoicing
data are only partly available (Jahn et al., 2022).

@@

\begin{itemize}
\tightlist
\item
  What was the number and proportion of open access articles in hybrid
  journals in transformative agreements between 2018 and 2022?
\item
  To what extent did institutions with a transformation agreement
  contribute to the adoption of open access in hybrid journals?
\end{itemize}

@@

After identifying hybrid journals included in transformative agreements,
article metadata were retrieved from the Crossref November 2023 database
snapshot for the five-year period from 2018 to 2022, according to the
issued date, representing the earliest known publication date. Because
Crossref metadata lacked information to distinguish between original
research articles, including reviews, and other types of journal
content, which are often not covered by transformative agreements
(Borrego et al., 2021), only articles published in regular issues
indicated by non-numeric pagination were included. Furthermore, an
expanded version of Unpaywall's paratext recognition approach was
applied to exclude non-scholarly journal content such as table of
contents.

@@

Comparing Crossref license coverage with OpenAlex, which re-uses open
access evidence from Unpaywall, a widely used open access discovery
service that also parses journal websites for open content licenses
(Piwowar et al., 2018), highlighted ongoing challenges in identifying
hybrid open access (Butler et al., 2023; Jahn et al., 2022;
Martín-Martín et al., 2018; Zhang et al., 2022). For the purpose of this
study, 742,369 articles under CC license were retrieved using Crossref,
while 950,260 articles were tagged as ``hybrid'' according to the
OpenAlex November 2023 release, which was used throughout this study.
The largest differences concerned articles published between 2018 and
2020. In 2022, however, Crossref and OpenAlex open access numbers differ
only slightly (249,511 records using Crossref vs.~255,344 in OpenAlex).
Notable differences could be observed among some publishers that
presumably did not provide CC license information to Crossref, including
AIP Publishing, the American Physiological Society, Emerald, and the
Royal Society. Crossref license metadata was more complete with regard
to the articles published by Wiley and the American Chemical Society.
Finally, inconsistent open access status information in previous
OpenAlex versions was observed (Jahn et al., 2023). After reporting this
to OpenAlex, fixing this issue was still ongoing according to the
release notes, which might also explain part of the discrepancy.

@@

Affiliation metadata about corresponding authors are crucial for the
planning and evaluation of transformative agreements because they are
considered responsible for arranging open access publication (Borrego et
al., 2021; Geschuhn \& Stone, 2017; Schimmer et al., 2015). For this
study, country and institutional affiliations were retrieved from
OpenAlex. However, because corresponding author affiliation was only
available for 54\% of the investigated articles in OpenAlex, this study
focused on first authors and their affiliations instead; approximately
90\% of the investigated articles had first author affiliation metadata
in OpenAlex. First authors typically contribute the most to a paper and
are often considered being lead authors (Larivière et al., 2016).
Related studies also assumed first authors as a proxy to measure open
access payments and the impact of transformative agreements (Haucap et
al., 2021; Shu \& Larivière, 2023; Zhang et al., 2022).

To assess the impact of transformative agreements on hybrid open access,
participating institutions from the Transformative Agreement Data dump,
which were crowd-sourced from the agreements and consortia that
successfully negotiated an agreement, were matched with the first author
affiliations recorded by OpenAlex using the ROR-ID. Matching also
considered the duration of agreements according to the ESAC registry.
Upon inspection, Transformative Agreement Data did not comprehensively
cover associated institutions, such as university hospitals or
institutes of large research organisations such as the Max Planck
Society. To improve the matching, Transformative Agreement Data were
automatically enriched with associated organisations using OpenAlex's
institution entity data.

@@

Throughout this mostly automated data gathering and analysis process,
Tidyverse tools (Wickham et al., 2019) for the R programming language (R
Core Team, 2020) were used. The resulting data are openly available
through an R data package, hoaddata (Jahn, 2023). Following Marwick et
al. (2018), hoaddata contains not only the datasets used in the data
analysis. It also includes code used to compile the data by connecting
it to the cloud-based Google Big Query data warehouse, where scholarly
big data from Crossref, OpenAlex and Unpaywall were imported, using
bigrquery (Wickham \& Bryan, 2020). To increase computational
reproducibility, data aggregation through hoaddata was automatically
carried out using GitHub Actions, a continuous integration service.

@@

Between 2018 and 2022, 11,189 out of 12,857 hybrid journals in
transformative agreements published at least one open access article
under a Creative Commons license. During this period, these hybrid
journals provided open access to 742,369 of the 8,146,958 articles,
representing a five-year open access proportion of 9.1\%. Authors who
could make use of transformative agreements at the time of publication
contributed 328,957 open access articles. Overall, 394 transformative
agreements recorded at least one open access article from an eligible
institution.

@@

Figure \ref{fig:results_overview}B highlights that the majority of
hybrid open access was made available through transformative agreements
in 2021 and 2022, contributing 58\% of the total open access article
volume in 2022. However, there was also a notable increase in open
access provision through other means, presumably publication fees being
not invoiced through transformative agreements, from 4.1\% (n = 62,625)
in 2018 to 6.3\% (n = 105,896).

@@

Despite the rise of open access across OECD countries, the overall
publication output decreased sharply, dropping to 786,903 in 2022 after
peaking 892,197 articles in 2020. In stark contrast, the number of
articles published in hybrid journals by first authors affiliated with
institutions from BRICS countries increased steadily over the years,
more than doubling from 356,632 in 2018 to 786,903 in 2022. Upon closer
examination, this trend can be observed across all of the three largest
publishers, although the shift towards BRICS is particularly evident in
Elsevier's hybrid journal portfolio, particularly with regard to
articles published in Physical Sciences journals. While OECD publication
output in Elsevier's Physical Sciences journals declined from 112,822
articles in 2018 to 103,766 in 2022, BRICS output increased from 104,654
to 171,713 in the same five-year period. Furthermore, OECD publication
output in Health Science Journals and Life Science journals stagnated
across the investigated hybrid journal portfolios after peaking in 2020.

@@

To illustrate the situation in 2022, Figure \ref{fig:country_patch}B
compares the total publication output with the number of open access
articles. With 391,530 articles, China was the most productive country,
followed by the United States (268,965 articles) and India (87,428
articles). In contrast, Western and Northern European countries
published a considerably high number of open access articles.
Particularly, Scandinavian countries, the Netherlands and Austria
recorded above-average open access shares, as indicated by the linear
trend line. As shown in Figure \ref{fig:country_patch}C, transformative
agreements contributed to these market positions. Interestingly, the
United States had a notable open access market share of 15\%, although
transformative agreements contributed to a lesser extent. Similarly,
China's open access market share of 7.2\% in 2022 was comparable to that
of the Netherlands, which was 7.1\%.

@@

\caption{Development of open access in hybrid journals in transformative agreements between 2018 and 2022, by the Top 20 most productive countries in terms of total articles published in the five-years period. Blue areas represent open access through transformative agreements, the grey areas depict open access articles where no link to an agreement could be established. Country names are represented as ISO two-letter country codes}\label{fig:country_top_20_plot}
\end{figure}

Since 2021, there has been a general trend towards hybrid open access
among many high-income countries, driven primarily by transformative
agreements. However, the proliferation of transformative agreements
differed across these countries. \# For instance, Germany successfully
negotiated an agreement with Elsevier not until 2023. Additionally,
publication limits or eligibility criteria for institutions and article
types may explain why even countries with widespread agreement
implementation such as Sweden or the Netherlands did not achieve 100\%
hybrid open access. Interestingly, in Japan and the United States,
options other than transformative agreements were the main drivers for
the increase in hybrid open access. Once again, the graph highlights
countries with low hybrid open access, particularly non-OECD countries,
where only a few or no agreements were in place.

@@

This large-scale study provides the first empirical evidence of the
influence of transformative agreements on the transition of hybrid
journals to full open access. However, several limitations needs to be
acknowledged. From a data perspective, estimations of open access
through transformative agreements were established by linking first
author affiliations with publicly available agreement data from
cOAlition S, and not through invoicing data, which is usually not
shared. Moreover, this study is unable to account for the various types
of transformative agreements, particularly with regard to article types
and caps that limit the number of open access articles covered.
Furthermore, assessing the quality of the OpenAlex and Crossref data
used, particularly in terms of affiliations and article types, by
comparing them with established bibliometric databases such as Scopus
and Web of Science was beyond the scope of this analysis. Overall, the
methodology is designed in such a way that the results underestimate
rather than overestimate the adoption of open access through
transformative agreements. In addition, the data used in this study are
openly available, along with the code used for this analysis.

Additionally, it must be noted that the study period was significantly
impacted by the COVID-19 pandemic, which led to an unprecedented number
of publications and a reduction in international collaboration
(Aviv-Reuven \& Rosenfeld, 2021), which could explain the observed
contrasting developments in OECD and BRICS countries. Even before the
pandemic, growth in publications in Europe was only due to
internationally co-authored journal articles (Kwiek, 2021). Likewise,
inflows from China to the US and European countries already declined by
2020 (Zhao et al., 2023). Furthermore, the study design did not consider
emerging publication practices such as preprints (Fraser et al., 2021)
and special issues (Hanson et al., 2023), which have grown rapidly since
2020. Lastly, it should be emphasised that the study did not address
financial shifts between subscriptions spending and open access payments
while analysing hybrid open access through transformative agreements due
to a lack of data on expenditures.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Brainard_2023}{}}%
Brainard, J. (2023). {``Transformative''} journals get booted for
switching to open access too slowly. \emph{Science}.
\url{https://doi.org/10.1126/science.adj3282}

@@

\leavevmode\vadjust pre{\hypertarget{ref-Geschuhn_2017}{}}%
Geschuhn, K., \& Stone, G. (2017). It's the workflows, stupid! What is
required to make {``offsetting''} work for the open access transition.
\emph{Insights the {UKSG} Journal}, \emph{30}(3), 103--114.
\url{https://doi.org/10.1629/uksg.391}

@@

\leavevmode\vadjust pre{\hypertarget{ref-Goodin_2023}{}}%
Rasmussen, K. B. (2023). Interview with {Robert {``Bob''} E. Goodin}.
\emph{Tidskrift För Politisk Filosofi}.
\url{https://www.politiskfilosofi.se/fulltext/2023-2/pdf/TPF_2023-2_interview_with_robert_bob_e_goodin.pdf}

@@

@@

\leavevmode\vadjust pre{\hypertarget{ref-bigrquery}{}}%
Wickham, H., \& Bryan, J. (2020). \emph{{bigrquery}: An interface to
{Google's BigQuery API}}.
\url{https://CRAN.R-project.org/package=bigrquery}

>>>>

\authornote{ORCID: https://orcid.org/0000-0001-5105-1463}

\abstract{The ongoing controversy surrounding transformative agreements, which aim to transition journal publishing to full open access, highlight the need for large-scale studies assessing the uptake of open access in hybrid journals. This includes evaluating the extent to which transformative agreements enabled open access. By combining publicly available data from various sources, including cOAlition S Journal Checker, Crossref, and OpenAlex, this study presents a novel approach that analyses over 700 agreements and nine million journal articles published in more than 11.000 hybrid journals. Estimates suggest a strong growth in open access between 2018 and 2022 from 4.3\% to 15\%. In 2022, 58\% of hybrid open access was enabled by transformative agreements. This trend was largely driven by the three commercial publishers Elsevier, Springer Nature, and Wiley, but the open access uptake varied substantially across journals, publishers, disciplines, and country affiliations. In particular, comparing the developments in the OECD and BRICS areas revealed different publication trends relative to hybrid open access. In conclusion, estimates suggest that current levels of implementation of transformative agreements is insufficient to bring about a large-scale transition to full open access.}

\keywords{hybrid open access, transformative agreements, scholarly publishing, big deals, bibliometrics}

@@

Despite these controversies around transformative agreements as a means
of transitioning journal publishing to full open access, there is
limited evidence available on the uptake of open access in hybrid
journals, and the extent to which this can be attributed to
transformative agreements. Previous studies have focused on specific
countries (Haucap et al., 2021; Huang et al., 2020; Pölönen et al.,
2020; Taubert et al., 2023; Wenaas, 2022) or publisher portfolios
(Bakker et al., 2024; Fraser et al., 2023; Jahn et al., 2022; Momeni et
al., 2023; Pieper \& Broschinski, 2018; Schmal, 2024), while large-scale
studies relied on self-reported agreement data (Moskovkin et al., 2022),
or used APC pricing lists (Shu \& Larivière, 2023). In particular, data
availability is a limiting factor when studying the impact of
transformative agreements (Bakker et al., 2024), because bibliometric
databases, even though many allow the retrieval of open access articles
in hybrid journals, do not directly attribute them to specific
transformative agreements. Likewise, article-level open access invoicing
data are only partly available (Jahn et al., 2022).

@@

\begin{itemize}
\tightlist
\item
  What was the number and proportion of open access articles in hybrid
  journals in transformative agreements between 2018 and 2022?
\item
  To what extent did institutions with a transformation agreement
  contribute to open access in hybrid journals?
\end{itemize}

@@

After identifying hybrid journals included in transformative agreements,
article metadata were retrieved from the Crossref November 2023 database
snapshot for the five-year period from 2018 to 2022, according to the
issued date, representing the earliest known publication date. Because
Crossref metadata lacked information to distinguish between original
research articles, including reviews, and other types of journal
content, which are often not covered by transformative agreements
(Borrego et al., 2021), only articles published in regular issues
indicated by non-numeric pagination were included. Furthermore, paratext
recognition was applied to exclude non-scholarly journal content such as
table of contents.

@@

Comparing Crossref license coverage with OpenAlex, which re-uses open
access evidence from Unpaywall, a widely used open access discovery
service that also parses journal websites for open content licenses
(Piwowar et al., 2018), highlighted ongoing challenges in identifying
hybrid open access (Butler et al., 2023; Jahn et al., 2022;
Martín-Martín et al., 2018; Zhang et al., 2022). For the purpose of this
study, 742,369 articles under CC license were retrieved using Crossref,
while 950,260 articles were tagged as ``hybrid'' according to the
OpenAlex November 2023 release, which was used throughout this study.
The largest differences concerned articles published between 2018 and
2020. With regard to the publication year 2022, however, Crossref and
OpenAlex open access numbers differ only slightly (249,511 records using
Crossref vs.~255,344 in OpenAlex). Notable differences could be observed
among some publishers that presumably did not provide CC license
information to Crossref, including AIP Publishing, the American
Physiological Society, Emerald, and the Royal Society. Crossref license
metadata was more complete with regard to the articles published by
Wiley and the American Chemical Society. Finally, inconsistent open
access status information in previous OpenAlex versions was observed
(Jahn et al., 2023). After reporting this to OpenAlex, fixing this issue
was still ongoing according to the release notes, which might also
explain part of the discrepancy.

@@

Affiliation metadata about corresponding authors are crucial for the
planning and evaluation of transformative agreements because they are
considered responsible for arranging open access publication (Borrego et
al., 2021; Geschuhn \& Stone, 2017; Schimmer et al., 2015). For this
study, country and institutional affiliations were retrieved from
OpenAlex. However, because corresponding author affiliation was only
available for 54\% of the investigated articles in OpenAlex, this study
focused on first authors and their affiliations instead; approximately
90\% of the investigated articles had first author affiliation metadata
in OpenAlex, which is a much larger proportion than previoulsy reported
for the October 2022 snapshot (Zhang et al., 2024). First authors
typically contribute the most to a paper and are often considered being
lead authors (Larivière et al., 2016). Related studies also assumed
first authors as a proxy to examine open access payments and
transformative agreements (Haucap et al., 2021; Shu \& Larivière, 2023;
Zhang et al., 2022).

To estimate the impact of transformative agreements on hybrid open
access, participating institutions from the Transformative Agreement
Data dump, which the cOAlition S crowd-sourced from agreement documents
and consortia, were matched with the first author affiliations recorded
by OpenAlex using the ROR-ID. Matching also considered the duration of
agreements according to the ESAC registry. Upon inspection,
Transformative Agreement Data did not comprehensively cover associated
institutions, such as university hospitals or institutes of large
research organisations such as the Max Planck Society. To improve the
matching, Transformative Agreement Data were automatically enriched with
associated organisations using OpenAlex's institution entity data.

@@

Throughout this mostly automated data gathering and analysis process,
Tidyverse tools (Wickham et al., 2019) for the R programming language (R
Core Team, 2020) were used. The resulting data are openly available
through an R data package, hoaddata (Jahn, 2023). Following Marwick et
al. (2018), hoaddata contains not only the datasets used in the data
analysis. It also includes code used to compile the data by connecting
it to the cloud-based Google Big Query data warehouse, where scholarly
big data from Crossref, OpenAlex and Unpaywall were imported, using
bigrquery (Wickham \& Bryan, 2023). To increase computational
reproducibility, data aggregation through hoaddata was automatically
carried out using GitHub Actions, a continuous integration service.

@@

Between 2018 and 2022, 11,189 out of 12,857 hybrid journals in
transformative agreements published at least one open access article
under a Creative Commons license. During this period, these hybrid
journals provided open access to 742,369 out of 8,146,958 articles,
representing a five-year open access proportion of 9.1\%. Authors who
could make use of transformative agreements at the time of publication
contributed 328,957 open access articles. Overall, 394 transformative
agreements recorded at least one open access article from an eligible
institution.

@@

Figure \ref{fig:results_overview}B highlights that the majority of
hybrid open access was made available through transformative agreements
in 2021 and 2022, contributing 58\% of the total open access article
volume in 2022. However, there was also a notable increase in open
access provision through other means, presumably publication fees being
not invoiced through transformative agreements, from 4.1\% (n = 62,625)
in 2018 to 6.3\% (n = 105,896) in 2022.

@@

Despite the rise of open access across OECD countries, the overall
publication output decreased sharply, dropping to 786,903 in 2022 after
peaking 892,197 articles in 2020. In stark contrast, the number of
articles published in hybrid journals by first authors affiliated with
institutions from BRICS countries increased steadily over the years,
more than doubling from 356,632 in 2018 to 786,903 in 2022. Upon closer
examination, this trend can be observed across all of the three largest
publishers, although the shift towards BRICS is particularly evident in
Elsevier's hybrid journal portfolio, particularly with regard to
articles published in Physical Sciences journals. While OECD publication
output in Elsevier's Physical Sciences journals declined from 112,822
articles in 2018 to 103,766 in 2022, BRICS output increased from 104,654
to 171,713 in the same five-year period. Furthermore, OECD publication
output in Health Sciences and Life Sciences journals stagnated after
peaking in 2020.

@@

To illustrate the situation in 2022, Figure \ref{fig:country_patch}B
compares the total publication output with the number of open access
articles. With 391,530 articles, China was the most productive country,
followed by the United States (n = 268,965) and India (n = 87,428). In
contrast, Western and Northern European countries published a
considerably high number of open access articles. Particularly,
Scandinavian countries, the Netherlands and Austria recorded
above-average open access shares, as indicated by the linear trend line.
As shown in Figure \ref{fig:country_patch}C, transformative agreements
contributed to these market positions. Interestingly, the United States
had a notable open access market share of 15\%, although transformative
agreements contributed to a lesser extent. Similarly, China's open
access market share of 7.2\% in 2022 was comparable to that of the
Netherlands, which was 7.1\%.

@@

\caption{Development of open access in hybrid journals in transformative agreements between 2018 and 2022, by the Top 20 most productive countries in terms of total articles published in the five-years period. Blue areas represent open access through transformative agreements, the grey areas depict open access articles where no link to an agreement could be established. Country names are represented as ISO two-letter country codes. Facet subheadings show the total number of articles and corresponding market share.}\label{fig:country_top_20_plot}
\end{figure}

Since 2021, there has been a general trend towards hybrid open access
among many high-income countries, driven primarily by transformative
agreements. However, the proliferation of transformative agreements
differed across these countries. Additionally, publication limits or
eligibility criteria for institutions and article types may explain why
even countries with widespread agreement implementation such as Sweden
or the Netherlands did not achieve 100\% hybrid open access.
Interestingly, in Japan and the United States, options other than
transformative agreements were the main drivers for the increase in
hybrid open access. Once again, the graph highlights countries with low
hybrid open access, particularly non-OECD countries, where only a few or
no agreements were in place.

@@

This large-scale study provides the first empirical evidence of the
influence of transformative agreements on the transition of hybrid
journals to full open access. However, several limitations needs to be
acknowledged. From a data perspective, estimations of open access
through transformative agreements were established by linking first
author affiliations with publicly available agreement data from
cOAlition S, and not through invoicing data, which is usually not
shared. Moreover, this study is unable to account for the various types
of transformative agreements, particularly with regard to article types
and caps that limit the number of open access articles covered.
Furthermore, assessing the quality of the OpenAlex and Crossref data
used, particularly in terms of affiliations and article types, by
combining them with established bibliometric databases such as Scopus
and Web of Science was beyond the scope of this analysis (Visser et al.,
2021). Overall, the methodology is designed in such a way that the
results underestimate rather than overestimate the adoption of open
access through transformative agreements. In addition, the data used in
this study are openly available, along with the code used for this
analysis.

Additionally, it must be noted that the study period was significantly
impacted by the COVID-19 pandemic, which led to an unprecedented number
of publications and a reduction in international collaboration
(Aviv-Reuven \& Rosenfeld, 2021), which could explain the observed
contrasting developments in OECD and BRICS countries. However, even
before the pandemic, growth in publications in Europe was only due to
internationally co-authored journal articles (Kwiek, 2021). Likewise,
inflows from China to the United States and European countries already
declined by 2020 (Zhao et al., 2023). Furthermore, the study design did
not consider emerging publication practices such as preprints (Fraser et
al., 2021) and special issues (Hanson et al., 2023), which have grown
rapidly since 2020. Lastly, it should be emphasised that the study did
not address financial shifts between subscriptions spending and open
access payments while analysing hybrid open access through
transformative agreements due to a lack of data on expenditures.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Brainard_2023}{}}%
Brainard, J. (2023). {`Transformative'} journals get booted for
switching to open access too slowly. \emph{Science}.
\url{https://doi.org/10.1126/science.adj3282}

@@

\leavevmode\vadjust pre{\hypertarget{ref-Geschuhn_2017}{}}%
Geschuhn, K., \& Stone, G. (2017). It's the workflows, stupid! What is
required to make {`offsetting'} work for the open access transition.
\emph{Insights the {UKSG} Journal}, \emph{30}(3), 103--114.
\url{https://doi.org/10.1629/uksg.391}

@@

\leavevmode\vadjust pre{\hypertarget{ref-Goodin_2023}{}}%
Rasmussen, K. B. (2023). Interview with {Robert {`Bob'} E. Goodin}.
\emph{Tidskrift För Politisk Filosofi}.
\url{https://www.politiskfilosofi.se/fulltext/2023-2/pdf/TPF_2023-2_interview_with_robert_bob_e_goodin.pdf}

@@

\leavevmode\vadjust pre{\hypertarget{ref-Visser_2021}{}}%
Visser, M., Eck, N. J. van, \& Waltman, L. (2021). Large-scale
comparison of bibliographic data sources: {Scopus, Web of Science,
Dimensions, Crossref, and Microsoft Academic}. \emph{Quantitative
Science Studies}, \emph{2}(1), 20--41.
\url{https://doi.org/10.1162/qss_a_00112}

@@

\leavevmode\vadjust pre{\hypertarget{ref-bigrquery}{}}%
Wickham, H., \& Bryan, J. (2023). \emph{Bigrquery: An interface to
google's 'BigQuery' 'API'}.
\url{https://CRAN.R-project.org/package=bigrquery}

\leavevmode\vadjust pre{\hypertarget{ref-Zhang_2024}{}}%
Zhang, L., Cao, Z., Shang, Y., Sivertsen, G., \& Huang, Y. (2024).
Missing institutions in OpenAlex: Possible reasons, implications, and
solutions. \emph{Scientometrics}.
\url{https://doi.org/10.1007/s11192-023-04923-y}
